The Development of Abstract Concepts in Children's Early Lexical Networks

### 2019-04-04 CMCL/ms.Rmd
final

---
title: "The development of abstract concepts in children's early lexical networks"

author-information: > 
    \author{{\large \bf Author 1} \\ \texttt{author1@university.edu} \\ Department of Psychology \\ Some University
    \And {\large \bf Author 2} \\ \texttt{author1@university.edu} \\ Department of Psychology \\ Some University}

@@

final_submission: no
# If yes, uncomment line below and add your own ID
# eaclpaperid: "1234"

@@

<!--On the other hand, children can track co-occurrence statistics \cite{saffran1996} and there is evidence that they use co-occurrence to make category-based generalization \cite{fisher2011,matlen2015}. 
Here we investigate the way abstract concepts may develop from the interaction of the children developing lexicon and co-occurrence information in the caregiver's speech. 
-->
We study development in light of two hypothetical models. On the first, called the simultaneous model, learning starts by exploring all parts of the conceptual space; categories are refined simultaneously over development. On the second, called the sequential model, learning starts by exploring a small region of the conceptual space (e.g., the category "animals") and only after the refinement of this category, does the learner move to another.

@@

## Constructing lexical networks

@@

## Identifying abstract concepts in a network

@@

## Measuring conceptual development

@@

$$
R(\mathcal{C}_t) = \frac{|tp(\mathcal{C}_t)|}{|tp(\mathcal{C}_t)| + |fn(\mathcal{C}_t)|}
$$
Where $tp(\mathcal{C}_t)$ are the true positives, defined as the word pairs that are placed in the same cluster under $\mathcal{C}_t$ and in the same cluster under $\mathcal{C}^*$. $fp(\mathcal{C}_t)$ are the false positives defined as the pairs placed in the same cluster under $\mathcal{C}_t$ and in different clusters under $\mathcal{C}^*$. Finally, $fn(\mathcal{C}_t)$ are the false positives defined as the pairs placed in different clusters under $\mathcal{C}_t$ and in the same cluster under $\mathcal{C}^*$.

We made this comparison using different degrees of clustering granularity. More precisely, we fixed the same number of clusters for *both* $\mathcal{C}_t$ and $\mathcal{C}^*$, and we varied this number from two to four clusters. We did not use the trivial case of one cluster, nor did we did use more than four clusters, since this number was optimal for the largest network (i.e., the end-state network) based on the modularity maximization criterion \cite{newman2006}.

## Learning mechanisms

We examined how abstract concepts develop under an average word learning trajectory derived from real developmental data. To construct this trajectory, we used the normative age of acquisition, that is, the age at which a word is produced by at least 50% of children in each language \cite{goodman2008}. We compared this development to the development induced by a simultaneous model and the development induced by a sequential model.

The simultaneous model was instantiated as a uniform sampling across time from the end-state vocabulary. The sequential model had the additional constraint of sampling from one category at a time: the first word is selected randomly from one cluster, subsequent words are sampled from the same cluster. After all words from this cluster are used, a word from a different cluster is chosen, and the same process is repeated until all clusters are covered.

@@

\vspace{1em} \fbox{\parbox[b][][c]{7.3cm}{\centering All data and code will be available online}} \vspace{1em}

>>>>

---
title: "The Development of Abstract Concepts in Children's Early Lexical Networks"

author-information: > 
    \author{{\large \bf Abdellah Fourtassi *} 
    \qquad {\large \bf Isaac L. Scheinfeld *}
    \qquad {\large \bf Michael C. Frank} \\ \texttt{\{afourtas, ischeinfeld, mcfrank\}@stanford.edu} \\ Department of Psychology \\ Stanford University}

@@

final_submission: yes
# If yes, uncomment line below and add your own ID
# eaclpaperid: "1234"

@@

<!--On the other hand, children can track co-occurrence statistics \cite{saffran1996} and there is evidence that they use co-occurrence to make category-based generalization \cite{fisher2011,matlen2015}. 
Here we investigate the way abstract concepts may develop from the interaction of the children developing lexicon and co-occurrence information in the caregiver's speech. 
-->
We study the real conceptual development (i.e. as induced by the real trajectory of word learning) in comparison to two hypothetical developmental scenarios induced by two divergent proposals about the trajectory of word learning. On the first proposal, past lexical knowledge facilitates the future learning of related words, e.g., the word "cat" is more likely to be followed by another animal name than it is to be followed by a food name \cite{steyvers2005,borovsky2016}. On the second proposal, past lexical knowledge does not influence future learning, e.g., learning the word "cat" does not necessarily increase the odds that the next word will be another animal name  \cite{hills2009,sizemore2018}.

@@

## Constructing Lexical Networks

@@

## Identifying Abstract Concepts in a Network

@@

## Measuring Conceptual Development

@@

$$
R(\mathcal{C}_t) = \frac{|tp(\mathcal{C}_t)|}{|tp(\mathcal{C}_t)| + |fn(\mathcal{C}_t)|}
$$
Where $tp(\mathcal{C}_t)$ are the true positives, defined as the word pairs that are placed in the same cluster under $\mathcal{C}_t$ and in the same cluster under $\mathcal{C}^*$. $fp(\mathcal{C}_t)$ are the false positives defined as the pairs placed in the same cluster under $\mathcal{C}_t$ and in different clusters under $\mathcal{C}^*$. Finally, $fn(\mathcal{C}_t)$ are the false negatives defined as the pairs placed in different clusters under $\mathcal{C}_t$ and in the same cluster under $\mathcal{C}^*$.

We made this comparison using different degrees of clustering granularity. More precisely, we fixed the same number of clusters for *both* $\mathcal{C}_t$ and $\mathcal{C}^*$, and we varied this number from two to four clusters. We did not use the trivial case of one cluster, nor did we use more than four clusters, since this number was optimal for the largest network (i.e., the end-state network) based on the modularity maximization criterion \cite{newman2006}.

## Learning Mechanisms

We examined how abstract concepts develop under an average word learning trajectory derived from real developmental data. To construct this trajectory, we used the normative age of acquisition, that is, the age at which a word is produced by at least 50% of children in each language \cite{goodman2008}. As mentioned above, we compared this development to the development induced by a first hypothetical trajectory where known words influence future word learning and a second hypothetical trajectory where learning proceeds regardless of what words are already known.

We instantiated the first trajectory through sampling from one conceptual category at a time: the first word is selected randomly from one cluster, subsequent words are sampled from the same cluster. After all words from this cluster are used, a word from a different cluster is chosen, and the same process is repeated until all clusters are covered. We call this sampling procedure the *sequential model*. We instantiated the second trajectory through a uniform sampling across time from the end-state vocabulary. We call this sampling procedure the *simultaneous model*.

@@

\vspace{1em} \fbox{\parbox[b][][c]{7.3cm}{\centering All data and code are available at https://github.com/afourtassi/conceptNet}} \vspace{1em}

### 2019-04-04 CMCL/ms.tex
final

% If you have:
%   final_submission: yes
%   eaclpaperid: <your ID number>
% in the .Rmd metadata, it should have automatically
% added "\eaclfinalcopy" and "\def\eaclpaperid{<your ID number>}" above

@@

\title{The development of abstract concepts in children's early lexical
networks}

\author{{\large \bf Author 1} \\ \texttt{author1@university.edu} \\ Department of Psychology \\ Some University \And {\large \bf Author 2} \\ \texttt{author1@university.edu} \\ Department of Psychology \\ Some University}

@@

We study development in light of two hypothetical models. On the first,
called the simultaneous model, learning starts by exploring all parts of
the conceptual space; categories are refined simultaneously over
development. On the second, called the sequential model, learning starts
by exploring a small region of the conceptual space (e.g., the category
``animals'') and only after the refinement of this category, does the
learner move to another.

@@

\subsection{Constructing lexical
networks}\label{constructing-lexical-networks}

@@

\subsection{Identifying abstract concepts in a
network}\label{identifying-abstract-concepts-in-a-network}

@@

\subsection{Measuring conceptual
development}\label{measuring-conceptual-development}

@@

\[
R(\mathcal{C}_t) = \frac{|tp(\mathcal{C}_t)|}{|tp(\mathcal{C}_t)| + |fn(\mathcal{C}_t)|}
\] Where \(tp(\mathcal{C}_t)\) are the true positives, defined as the
word pairs that are placed in the same cluster under \(\mathcal{C}_t\)
and in the same cluster under \(\mathcal{C}^*\). \(fp(\mathcal{C}_t)\)
are the false positives defined as the pairs placed in the same cluster
under \(\mathcal{C}_t\) and in different clusters under
\(\mathcal{C}^*\). Finally, \(fn(\mathcal{C}_t)\) are the false
positives defined as the pairs placed in different clusters under
\(\mathcal{C}_t\) and in the same cluster under \(\mathcal{C}^*\).

We made this comparison using different degrees of clustering
granularity. More precisely, we fixed the same number of clusters for
\emph{both} \(\mathcal{C}_t\) and \(\mathcal{C}^*\), and we varied this
number from two to four clusters. We did not use the trivial case of one
cluster, nor did we did use more than four clusters, since this number
was optimal for the largest network (i.e., the end-state network) based
on the modularity maximization criterion \cite{newman2006}.

\subsection{Learning mechanisms}\label{learning-mechanisms}

We examined how abstract concepts develop under an average word learning
trajectory derived from real developmental data. To construct this
trajectory, we used the normative age of acquisition, that is, the age
at which a word is produced by at least 50\% of children in each
language \cite{goodman2008}. We compared this development to the
development induced by a simultaneous model and the development induced
by a sequential model.

The simultaneous model was instantiated as a uniform sampling across
time from the end-state vocabulary. The sequential model had the
additional constraint of sampling from one category at a time: the first
word is selected randomly from one cluster, subsequent words are sampled
from the same cluster. After all words from this cluster are used, a
word from a different cluster is chosen, and the same process is
repeated until all clusters are covered.

@@

\fbox{\parbox[b][][c]{7.3cm}{\centering All data and code will be available online}}
\vspace{1em}

>>>>

\eaclfinalcopy
\def\eaclpaperid{}
% If you have:
%   final_submission: yes
%   eaclpaperid: <your ID number>
% in the .Rmd metadata, it should have automatically
% added "\eaclfinalcopy" and "\def\eaclpaperid{<your ID number>}" above

@@

\title{The Development of Abstract Concepts in Children's Early Lexical
Networks}

\author{{\large \bf Abdellah Fourtassi *}  \qquad {\large \bf Isaac L. Scheinfeld *} \qquad {\large \bf Michael C. Frank} \\ \texttt{\{afourtas, ischeinfeld, mcfrank\}@stanford.edu} \\ Department of Psychology \\ Stanford University}

@@

We study the real conceptual development (i.e.~as induced by the real
trajectory of word learning) in comparison to two hypothetical
developmental scenarios induced by two divergent proposals about the
trajectory of word learning. On the first proposal, past lexical
knowledge facilitates the future learning of related words, e.g., the
word ``cat'' is more likely to be followed by another animal name than
it is to be followed by a food name \cite{steyvers2005,borovsky2016}. On
the second proposal, past lexical knowledge does not influence future
learning, e.g., learning the word ``cat'' does not necessarily increase
the odds that the next word will be another animal name
\cite{hills2009,sizemore2018}.

@@

\subsection{Constructing Lexical
Networks}\label{constructing-lexical-networks}

@@

\subsection{Identifying Abstract Concepts in a
Network}\label{identifying-abstract-concepts-in-a-network}

@@

\subsection{Measuring Conceptual
Development}\label{measuring-conceptual-development}

@@

\[
R(\mathcal{C}_t) = \frac{|tp(\mathcal{C}_t)|}{|tp(\mathcal{C}_t)| + |fn(\mathcal{C}_t)|}
\] Where \(tp(\mathcal{C}_t)\) are the true positives, defined as the
word pairs that are placed in the same cluster under \(\mathcal{C}_t\)
and in the same cluster under \(\mathcal{C}^*\). \(fp(\mathcal{C}_t)\)
are the false positives defined as the pairs placed in the same cluster
under \(\mathcal{C}_t\) and in different clusters under
\(\mathcal{C}^*\). Finally, \(fn(\mathcal{C}_t)\) are the false
negatives defined as the pairs placed in different clusters under
\(\mathcal{C}_t\) and in the same cluster under \(\mathcal{C}^*\).

We made this comparison using different degrees of clustering
granularity. More precisely, we fixed the same number of clusters for
\emph{both} \(\mathcal{C}_t\) and \(\mathcal{C}^*\), and we varied this
number from two to four clusters. We did not use the trivial case of one
cluster, nor did we use more than four clusters, since this number was
optimal for the largest network (i.e., the end-state network) based on
the modularity maximization criterion \cite{newman2006}.

\subsection{Learning Mechanisms}\label{learning-mechanisms}

We examined how abstract concepts develop under an average word learning
trajectory derived from real developmental data. To construct this
trajectory, we used the normative age of acquisition, that is, the age
at which a word is produced by at least 50\% of children in each
language \cite{goodman2008}. As mentioned above, we compared this
development to the development induced by a first hypothetical
trajectory where known words influence future word learning and a second
hypothetical trajectory where learning proceeds regardless of what words
are already known.

We instantiated the first trajectory through sampling from one
conceptual category at a time: the first word is selected randomly from
one cluster, subsequent words are sampled from the same cluster. After
all words from this cluster are used, a word from a different cluster is
chosen, and the same process is repeated until all clusters are covered.
We call this sampling procedure the \emph{sequential model}. We
instantiated the second trajectory through a uniform sampling across
time from the end-state vocabulary. We call this sampling procedure the
\emph{simultaneous model}.

@@

\fbox{\parbox[b][][c]{7.3cm}{\centering All data and code are available at https://github.com/afourtassi/conceptNet}}
\vspace{1em}
